Place of death in NRS COVID-19 deaths: data processing for analysis

### 2021-10-01 covid_nrs_place_of_death_data.Rmd
updated LA boundaries shapefile since link changed; changed output directory creation to be recursive, otherwise it fails!

dir_outputs <- paste0("./outputs/",latest_data_modified_date)
if (!dir.exists(dir_outputs)) dir.create(dir_outputs)
```

@@

* Local Authority Districts (LAD) for 2020 (BUC-level resolution): https://geoportal.statistics.gov.uk/datasets/local-authority-districts-may-2020-boundaries-uk-buc
* Health Boards https://data.gov.uk/dataset/27d0fe5f-79bb-4116-aec9-a8e565ff756a/nhs-health-boards
  - Note: this is a fairly high resolution, don't need this much detail!
  - I found a discussion of this on [a github covid-related project](https://github.com/tomwhite/covid-19-uk-data/issues/18#issuecomment-622353841), and user **robchallen** produced a zip file containing [UK-wide health board boundaries](https://github.com/tomwhite/covid-19-uk-data/files/4563933/UK_covid_reporting_regions.zip)

>>>>

dir_outputs <- paste0("./outputs/",latest_data_modified_date)
if (!dir.exists(dir_outputs)) dir.create(dir_outputs, recursive = TRUE)
```

@@

* Local Authority Districts (LAD) for 2020 (BUC-level resolution): https://geoportal.statistics.gov.uk/datasets/local-authority-districts-december-2020-uk-buc/
* Health Boards https://data.gov.uk/dataset/27d0fe5f-79bb-4116-aec9-a8e565ff756a/nhs-health-boards
  - Note: this is a fairly high resolution, don't need this much detail!
  - I found a discussion of this on [a github covid-related project](https://github.com/tomwhite/covid-19-uk-data/issues/18#issuecomment-622353841), and user **robchallen** produced a zip file containing [UK-wide health board boundaries](https://github.com/tomwhite/covid-19-uk-data/files/4563933/UK_covid_reporting_regions.zip)
